\vspace{-1cm} Model linearity breeds contempt: using Bayesian non-linear models to uncover general biogeographical patterns

### 2021-03-05 manuscript/manuscript.tex
change mean

\subsubsection*{Heavy-tail and skewed response curve}
Finally, one could also consider a response curve with both kurtosis and skewness. A convenient way to achieve this is by considering a response curve that follows a skewed generalized error distribution (also see XX). This is a combination of the two distributions described above, containing two parameters that control for both the level and direction of kurtosis and skewness. The skewed generalized error distribution can be considered by modifying the species' response curve in Eq.~(\ref{eq:baseline-response}) as
\begin{equation}	
\begin{split}
\text{log}\left(p_{ij}\right) = -\alpha_{i} - \left(\frac{\gamma^{\prime}_{i}\,|x_{j}-\beta^{\prime}_{i}|}{1+\lambda_{i} \text{sgn}\left(x_{j}-\beta^{\prime}_{i}\right)}\right)^{\nu_{i}} ,
\end{split}
\label{eq:heavy-skewed-response}
\end{equation}
where $\gamma^{\prime}_{i} = f_{1}\left(\gamma_{i}, \nu_{i}, \lambda_{i}\right)$, $\beta^{\prime}_{i} = f_{2}\left(\gamma_{i}, \beta_{i}, \nu_{i}, \lambda_{i}\right)$, $\nu_{i}$ and $\lambda_i$ are parameters that describe the kurtosis and skewness of the distribution, respectively. $\text{sgn}\left(x\right)$ is the sign function. We define $\nu_i$ and its prior as in Eq.~\ref{eq:generalized-response}. However, $\lambda_i$ is now defined as $\lambda_{i}\in\left(-1, 1\right)$, with an adaptive prior such that $\text{logit}\left(2\lambda_{i}-1\right)\sim \text{Normal}\left(\hat{\lambda}, \sigma_{\lambda}\right)$, where $\hat{\lambda}\sim\text{Normal}\left(0, 1\right)$ and $\sigma_{\lambda}\sim\text{Exponential}\left(1\right)$. Again, we can re-parametrize the model following $f_1$ and $f_2$, and set the rest of the prior distributions as for the baseline model (see Supplementary Table 2; Code Availability section). Notice that the generalized error distribution (Eq.~\ref{eq:generalized-response}) and the skew normal distribution (Eq.~\ref{eq:skewed-response}) are special cases of Eq.~(\ref{eq:heavy-skewed-response}) when $\lambda_i=0$ and $\nu_i=2$, respectively.

>>>>

\subsubsection*{Heavy-tail and skewed response curve}
Finally, one could also consider a response curve with both kurtosis and skewness. A convenient way to achieve this is by considering a response curve that follows a skewed generalized error distribution (also see XX). This is a combination of the two distributions described above, containing two parameters that control for both the level and direction of kurtosis and skewness. The skewed generalized error distribution can be considered by modifying the species' response curve in Eq.~(\ref{eq:baseline-response}) as
\begin{equation}	
\begin{split}
\text{log}\left(p_{ij}\right) = -\alpha_{i} - \left(\frac{\gamma^{\prime}_{i}\,|x_{j}-\beta^{\prime}_{i}|}{1+\lambda_{i}\,\text{sgn}\left(x_{j}-\beta^{\prime}_{i}\right)}\right)^{\nu_{i}} ,
\end{split}
\label{eq:heavy-skewed-response}
\end{equation}
where $\gamma^{\prime}_{i} = f_{1}\left(\gamma_{i}, \nu_{i}, \lambda_{i}\right)$, $\beta^{\prime}_{i} = f_{2}\left(\gamma_{i}, \beta_{i}, \nu_{i}, \lambda_{i}\right)$, $\nu_{i}$ and $\lambda_i$ are parameters that describe the kurtosis and skewness of the distribution, respectively. $\text{sgn}\left(x\right)$ is the sign function. We define $\nu_i$ and its prior as in Eq.~\ref{eq:generalized-response}. However, $\lambda_i$ is now defined as $\lambda_{i}\in\left(-1, 1\right)$, with an adaptive prior such that $\text{logit}\left(\frac{\lambda_{i}+1}{2}\right)\sim \text{Normal}\left(\hat{\lambda}, \sigma_{\lambda}\right)$, where $\hat{\lambda}\sim\text{Normal}\left(0, 1\right)$ and $\sigma_{\lambda}\sim\text{Exponential}\left(1\right)$. Again, we can re-parametrize the model following $f_1$ and $f_2$, and set the rest of the prior distributions as for the baseline model (see Supplementary Table 2; Code Availability section). Notice that the generalized error distribution (Eq.~\ref{eq:generalized-response}) and the skew normal distribution (Eq.~\ref{eq:skewed-response}) are special cases of Eq.~(\ref{eq:heavy-skewed-response}) when $\lambda_i=0$ and $\nu_i=2$, respectively.
